%===== General Conclusion =====%

\chapter*{General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion}
\markboth{GENERAL CONCLUSION}{}

\section*{Summary of Achievements}

This project set out to design and build a production-ready, full-stack e-commerce
platform tailored for the Tunisian market. Over the course of the internship at
\textbf{Anter Lab}, the following was delivered:

\textbf{A three-service TypeScript platform:}
\begin{itemize}
    \item \texttt{malltech-backend} --- A NestJS 11 RESTful API with 14 feature modules covering every aspect of e-commerce: catalog, commerce, payments, CMS, authentication, notifications, analytics, locations, and real-time customer support. Backed by MongoDB 7.0 with Mongoose ODM.
    \item \texttt{malltech-frontend} --- A Next.js 16 customer storefront with SSR/SSG for SEO, a full shopping journey (browse $\rightarrow$ cart $\rightarrow$ checkout $\rightarrow$ order tracking), a wishlist, blog, and real-time support chat.
    \item \texttt{malltech-admin} --- A Next.js 16 backoffice dashboard providing full control over the catalog, order lifecycle, customer management, financial documents (invoices, credit notes), content (banners, blogs, site config), promotions, coupons, and analytics.
\end{itemize}

\textbf{Infrastructure and DevOps:}
\begin{itemize}
    \item Containerised deployment with Docker Compose on a single OVH VPS behind a Caddy reverse proxy with automatic HTTPS.
    \item Three independent GitHub Actions CI/CD pipelines (test $\rightarrow$ security scan $\rightarrow$ build $\rightarrow$ deploy $\rightarrow$ notify) with zero-downtime rolling updates and automatic rollback.
    \item Infrastructure-level monitoring with Netdata and a custom auto-healing shell script.
\end{itemize}

\textbf{Differentiating features for the Tunisian market:}
\begin{itemize}
    \item Governorate-based delivery with configurable shipping rates per governorate.
    \item Cash-at-selling-point payment workflow.
    \item Sequential invoice and credit-note PDF generation, fully server-side.
    \item Discord bot integration for customer support.
    \item Barcode lookup for rapid product data entry in the admin.
    \item 3D product model viewer for categories that benefit from spatial visualisation.
\end{itemize}

\section*{Challenges Encountered}

\textbf{Dual authentication coexistence:} Implementing both JWT (registered users)
and cookie sessions (guests) on the same NestJS application required careful
middleware and guard ordering to ensure sessions did not add overhead to pure JWT
routes while remaining available for guest basket operations.

\textbf{Atomic stock management:} Preventing overselling under concurrent order
placements without distributed transactions required leveraging MongoDB's atomic
\texttt{findOneAndUpdate} with a conditional filter (\texttt{quantity >= requested}).
Designing this correctly was critical for data integrity.

\textbf{Real-time support with Discord integration:} Bridging the WebSocket server
(Socket.IO) with the Discord API (Discord.js) in a bidirectional way required
careful event routing to ensure messages appeared in the browser chat and vice
versa, without duplication or loss.

\textbf{CI/CD rollback mechanism:} Implementing a reliable rollback in GitHub
Actions required snapshotting the previous image digest before pulling the new one,
so a failed health check could re-tag and restart the previous known-good image ---
all within a single SSH session.

\section*{Perspectives and Future Enhancements}

While Malltech is production-ready in its current form, several enhancements would
increase its commercial value:

\begin{longtable}{|m{4cm}|m{9.5cm}|}
    \hline
    \textbf{Enhancement} & \textbf{Description} \\
    \hline
    \endhead
    \endfoot
    \endlastfoot
    \hline
    Online payment integration & Integration with Tunisian payment gateways (Konnect, Flouci, Paymee) for card-based transactions. \\
    \hline
    Multi-vendor marketplace & Extend the platform to support multiple independent sellers with per-seller analytics and payouts. \\
    \hline
    Native mobile app & A React Native or Flutter app for iOS and Android, reusing the existing REST API. \\
    \hline
    Advanced search & Replace MongoDB text search with Meilisearch for richer filtering, typo tolerance, and faceted search. \\
    \hline
    Recommendation engine & ML-based product recommendations based on browsing history and purchase patterns. \\
    \hline
    Progressive Web App & Add service workers for offline support, push notifications, and home screen installation. \\
    \hline
    Horizontal scaling & Move session storage to Redis and file storage to MinIO/S3 to enable multi-instance API deployment. \\
    \hline
    Automated backup & Scheduled \texttt{mongodump} exports to S3-compatible storage for disaster recovery. \\
    \hline
    \caption{Planned future enhancements}
    \label{tab:enhancements}
\end{longtable}

\section*{Personal Reflection}

This internship provided hands-on experience with the complete software delivery
lifecycle --- from requirements analysis and architecture design, through full-stack
implementation across three codebases, to containerised deployment and CI/CD
automation. Building a real-world platform rather than a toy application forced
engagement with production concerns that textbooks rarely cover: race conditions
in inventory management, certificate automation, zero-downtime deployments, and
security scanning in CI. The result is a platform that is live, functional, and
ready to serve real customers.
