%===== General Introduction =====%

\chapter*{General Introduction}
\addcontentsline{toc}{chapter}{General Introduction}
\markboth{GENERAL INTRODUCTION}{}

\section*{Context}

The rapid growth of internet access and smartphone adoption across the MENA region
has transformed consumer behaviour. Tunisia, with a growing middle class and
increasing digital literacy, presents a fertile ground for e-commerce. Yet most
local merchants still rely on fragmented solutions --- social media shops, manual
invoicing, and phone-based order management --- that cannot scale, offer no
real-time inventory visibility, and provide a poor customer experience.

This project, \textbf{Malltech}, was undertaken as a second-year internship at
\textbf{Anter Lab} to design and build a production-grade, full-stack e-commerce
platform purpose-built for the Tunisian market, covering the complete commercial
lifecycle from product discovery to order fulfilment, invoicing, and after-sale support.

\section*{Problem Statement}

Existing e-commerce solutions available to Tunisian merchants are either generic
international platforms (Shopify, WooCommerce) that require significant configuration
overhead and do not natively handle local payment workflows, custom legacy systems
that are tightly coupled and hard to maintain, or social media storefronts that
provide zero inventory management or analytics.

The gap is a modern, self-hosted, open-architecture platform that:
\begin{enumerate}
    \item Handles the Tunisian commerce context (governorate-based delivery, local selling points, TND currency).
    \item Provides a polished customer-facing storefront with full-text search, promotions, and a wishlist.
    \item Offers a feature-complete administration dashboard.
    \item Can be maintained and extended by a small engineering team.
    \item Is deployable on affordable infrastructure with zero-downtime releases.
\end{enumerate}

\section*{Project Objectives}

\textbf{Primary objectives:}
\begin{itemize}
    \item Design and implement a RESTful API handling all business logic (catalog, commerce, authentication, support, CMS).
    \item Build a customer storefront covering the full shopping journey: browse $\rightarrow$ cart $\rightarrow$ checkout $\rightarrow$ order tracking.
    \item Build an administration dashboard covering catalog management, order processing, customer management, content publishing, and analytics.
\end{itemize}

\textbf{Secondary objectives:}
\begin{itemize}
    \item Implement a secure, dual authentication system: JWT for registered users, session-based tracking for guests.
    \item Integrate automated invoice and credit-note PDF generation.
    \item Provide real-time customer support via WebSocket and a Discord bot.
    \item Automate build, test, security scanning, and deployment via GitHub Actions CI/CD.
    \item Containerise all services with Docker behind a reverse proxy with automatic HTTPS.
    \item Set up infrastructure-level monitoring and auto-healing.
\end{itemize}

\section*{Scope and Limitations}

\textbf{In scope:} Full backend API (NestJS + MongoDB), customer storefront (Next.js),
admin backoffice (Next.js), Docker-based deployment on a single VPS, and CI/CD
pipelines for all three services.

\textbf{Out of scope:} Native mobile applications, third-party payment gateway
integration, multi-vendor marketplace functionality, and advanced ML-based
recommendations.

\section*{Report Organisation}

\begin{table}[H]
\centering
\begin{tabular}{|m{2.5cm}|m{4.5cm}|m{7cm}|}
    \hline
    \textbf{Chapter} & \textbf{Title} & \textbf{Content} \\
    \hline
    Chapter 1 & Project Framework and Context & Host company, methodology, existing solutions \\
    \hline
    Chapter 2 & Requirements Analysis & Actors, functional/non-functional requirements, use cases \\
    \hline
    Chapter 3 & System Design and Architecture & Global architecture, database models, API design \\
    \hline
    Chapter 4 & Implementation & Technology stack, module-by-module implementation \\
    \hline
    Chapter 5 & Testing and Deployment & Test strategy, CI/CD pipeline, infrastructure, monitoring \\
    \hline
\end{tabular}
\caption{Report structure}
\label{tab:report_structure}
\end{table}

The report closes with a general conclusion summarising achievements and prospective enhancements.
